Evaluation of the locality of the Mainline DHT

### 2014-05-29 paper.tex
updated paper

\section{Conclusion}
In this paper we have shown that locality in Mainline DHT can be achieved with a very simple routing policy bases on \textit{Proximity Neighbour Selection} with RTT measurements. We also show that Mainline DHT, as defined in BEP5, is designed specifically for Internet scale deployments, changes on the DHT dimensions are required in order to properly accommodate smaller deployments, for instance, thus on Community Networks.

>>>>

\section{Conclusion}
In this paper we have shown that locality in Mainline DHT can be achieved with a very simple routing policy based on \textit{Proximity Neighbour Selection} with RTT measurements. We also show that Mainline DHT, as defined in BEP5, is designed specifically for Internet scale deployments, changes on the DHT dimensions are required in order to properly accommodate smaller deployments, for instance, thus on Community Networks.
